# Introduction to R

### 0. Loading dataset

```{r}
library(ISLR)

data('Auto')

head(Auto)
```

### 1. Mean fuel consumption

```{r}
names(Auto)
```

```{r}
mean(Auto$mpg)
```

### 2. Mean fuel consumption of 4-cylinder cars

```{r}
mean(subset(Auto, cylinders == 4)$mpg)
```

### 3. Median of weight

```{r}
median(Auto$weight)
```

### 4. Fuel consumption of cars from year 72

```{r}
mean(subset(Auto, year == 72)$mpg)
```

### 5. Variation of acceleration

```{r}
var(Auto$acceleration)
```

### 6. Variation of acceleration in Japanese cars

```{r}
var(subset(Auto, origin ==3)$acceleration)
```

### 7. Number of cars with above average horsepower

```{r}
average_horsepower = mean(Auto$horsepower)
sum(Auto$horsepower > average_horsepower)
```

### 8. Max horsepower of light cars

```{r}
average_weight = mean(Auto$weight)
max(subset(Auto, weight < average_weight)$horsepower)
```

### 9. Number of cars with low fuel consumption

```{r}
average_mpg = mean(Auto$mpg)
sum(Auto$mpg > average_mpg)
```

### 10. Minimal cylinders of cars with low fuel consumption

```{r}
min(subset(Auto, mpg > average_mpg)$cylinders)
```

### 11. Number of cars with maximal displacement

```{r}
sum(Auto$displacement == max(Auto$displacement))
```

### 12. Max weight of car with displacment smaller then median

```{r}
max(subset(Auto, displacement < median(displacement))$weight)
```
